Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-27 prop_iop.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Use \sum to simplify the formula...

\begin{definition}~
\begin{itemize}
\item Consider a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
\item We still decompose a random variable~$X$ into step functions, but
we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
i.e., 
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint.
\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-f\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
\end{itemize}
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\sum_{i=1}^{N^{+}}x_{i}^{+}\left[\Delta\mul\left(E_{i}^{+\prime}\right),\Delta\mur\left(E_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}x_{i}^{-}\left[\Delta\mul\left(E_{i}^{-\prime}\right),\Delta\mur\left(E_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:interval-expectation}
\end{equation}
\end{definition}

The following lemma shows our definition is exactly the same as in
the literature.

@@

Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
can be considered as weighted average of the possible outcomes of
$X$ as well, despite the ``weight''
\begin{equation}
\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\subseteq\left[\mul\left(E_{i}^{s}\right),\mur\left(E_{i}^{s}\right)\right]=\bar{\mu}\left(E_{i}^{s}\right)\textrm{ for }s\in\left\{ +,-\right\} 
\end{equation}
is tighter than the interval-valued probability of the corresponding
event. Since only one event can happen at once, we don't have to be
so pessimistic to accumulate all possible fuzziness together, and
expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}^{s}\right)$ to happen.

@@

\begin{thm}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
is convex if and only if $\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]$.\end{thm}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectrum decomposition
\begin{equation}
\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
defined by $X=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\mathbf{1}_{\tau\left(P_{i}^{-}\right)}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}\mathbf{1}_{\tau\left(P_{i}^{+}\right)}$.
Then, 
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\\
 & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{+\prime}\right)\right)\right]+\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{-\prime}\right)\right)\right]\\
 & = & \int X\rmd\bar{\mu}'\\
 & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu\right]
\end{eqnarray*}
\end{proof}

>>>>

\begin{definition}\label{def:Choquet}~
\begin{itemize}
\item Consider a classical IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
\item We still decompose a random variable~$X$ into step functions, but
we separate the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
i.e., 
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint.
\item Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$ and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-f\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
\end{itemize}
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:interval-expectation}
\end{equation}
\end{definition}

\noindent The following lemma shows our definition is exactly the
same as in the literature.

@@

\noindent Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
can be considered as weighted average of the possible outcomes of
$X$ as well, despite the ``weight''
\begin{equation}
\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\subseteq\left[\mul\left(E_{i}^{s}\right),\mur\left(E_{i}^{s}\right)\right]=\bar{\mu}\left(E_{i}^{s}\right)\textrm{ for }s\in\left\{ +,-\right\} 
\end{equation}
is tighter than the interval-valued probability of the corresponding
event. Since only one event can happen at once, we don't have to be
so pessimistic to accumulate all possible fuzziness together, and
expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}^{s}\right)$ to happen.

@@

\begin{thm}\label{thm:Rosenmuller}\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}For
every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$ and
any random variable~$X:\Omega\rightarrow\mathbb{R}$, $\bar{\mu}$
is convex if and only if $\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]$.\end{thm}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{equation}

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}=\bar{\mu}'\circ\tau$. Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$
and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}'$, respectively, i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$.
Then, 
\begin{eqnarray*}
 &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & = & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
 & = & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
 & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
 & = & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
\end{eqnarray*}
where 
\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\le\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
because $\tau$ in theorem~\ref{thm:sub-event-space} applies to
both real-valued and interval-valued probability measure, for any
$\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)$, there exists
a $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that $\mu=\mu'\circ\tau$.
On the other hand, 
\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\ge\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)
because for any $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we
have 
\begin{eqnarray*}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray*}
Let $\rho=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}P_{i}^{s}$.
Then, we have 
\begin{eqnarray*}
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{-}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{-}\right)=\mu'\left(\tau\left(P_{j}^{-}\right)\right)\\
\mu_{\rho}^{\mathrm{B}}\left(P_{j}^{+}\right) & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\frac{\mu'\left(\tau\left(P_{i}^{s}\right)\right)}{\Tr\left(P_{i}^{s}\right)}\Tr\left(P_{i}^{s}P_{j}^{+}\right)=\mu'\left(\tau\left(P_{j}^{+}\right)\right)
\end{eqnarray*}
Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$.\end{proof}
